Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-05-22 talk/dls2014/paper/paper.tex
Comment

\newcommand\remi[1]{\mynote{Remi}{#1}}
\newcommand\cfbolz[1]{\mynote{cfbolz}{#1}}

@@

Our contributions include:
\begin{itemize}[noitemsep]
\item We introduce a new software transactional memory (STM) system
  that performs well even on low numbers of CPUs. It uses a novel
  combination of hardware features and garbage collector (GC)
  integration in order to keep the overhead of STM very low.
\item This new STM system is used to replace the GIL in Python and is
  then evaluated extensively.
\item We introduce atomic blocks to the Python language to provide a
  backwards compatible, composable synchronisation mechanism for
  threads.
\end{itemize}

>>>>

\newcommand\remi[1]{\mynote{Remi}{#1}}
\newcommand\cfbolz[1]{\mynote{cfbolz}{#1}}
\newcommand\arigo[1]{\mynote{arigo}{#1}}

@@

Our contributions include:
\begin{itemize}[noitemsep]
\item We introduce a new software transactional memory (STM) system
  that performs well even on low numbers of CPUs. It uses a novel
  combination of hardware features\arigo{"OS-level feature" maybe.
  "Hardware feature" implies it only works on custom chips}
  and garbage collector (GC)
  integration in order to keep the overhead of STM very low.
\item This new STM system is used to replace the GIL in Python and is
  then evaluated extensively.
\item We introduce atomic blocks to the Python language to provide a
  backwards compatible, composable synchronisation mechanism for
  threads.
\end{itemize}
